Contracts for unions and intersections are hard for Nickel

### 2021-05-30 paper.tex
Paper structure

\title{Contracts for unions and intersections are hard for Nickel}
\author{Teodoro Freund}
\affiliation{
  \institution{???}
  \city{Buenos Aires}
  \country{Argentina}
}
\email{???}
\author{Yann Hamdaoui}
\affiliation{
  \institution{Tweag}
  \city{Paris}
  \country{France}
}
\email{yann.hamdaoui@tweag.io}
\author{Arnaud Spiwack}
\affiliation{
  \institution{Tweag}
  \city{Paris}
  \country{France}
}
\email{arnaud.spiwack@tweag.io}

@@

\unsure{TODO: CCS classification; Keywords}
\section{Introduction}
\info{Goals of the paper: position paper: unions/intersections nice in
theory problematic in practice. In particular non-orthogonal with the
rest of the features of your language.}

@@

@@

\section{Features of languages}
\info{Zoology of various features that we will eventually show
  conflict with this or that property or implementation of union and
  intersection. Including user-define contracts.}

@@

\section{Union \& intersection}
\info{What are they, what are they used for.}

@@

\section{Issues coming from the semantics}
\info{What goes wrong or difficult when trying to implement union and
  intersection literally}

@@

\section{Issues in concrete restrictions from the literature}
\info{The various papers and the tradeoffs they make}

@@

\section{Related work}
\info{Including a mention of statically typed systems with union}
\info{Include something about Racket's and and or contracts}

@@

\section{Conclusion}

>>>>

\title{Contracts for unions and intersections are hard for Nickel}
\author{Teodoro Freund}
\affiliation{
  \institution{Universidad de Buenos Aires}
  \city{Buenos Aires}
  \country{Argentina}
}
\email{tfreund95@gmail.com}

\author{Yann Hamdaoui}
\affiliation{
  \institution{Tweag}
  \city{Paris}
  \country{France}
}
\email{yann.hamdaoui@tweag.io}
\author{Arnaud Spiwack}
\affiliation{
  \institution{Tweag}
  \city{Paris}
  \country{France}
}
\email{arnaud.spiwack@tweag.io}

@@

\unsure{TODO: CCS classification; Keywords}
\section{Introduction}
\label{sec:intro}
\info{Goals of the paper: position paper: unions/intersections nice in
theory problematic in practice. In particular non-orthogonal with the
rest of the features of your language.}

@@

\subsection*{Structure of this paper}
This paper is structured as follows, Section \ref{sec:intro} introduces
this paper; Section \ref{sec:feat-lang} outlines various features
of programming languages that may interact badly with union and intersection
contracts.
Section \ref{sec:union-inter} gives a primer on Unions and Intersections,
enough to understand this work.

Section \ref{sec:issues-sem} shows what difficulties or issues, proper of
unions and intersections, one may
encounter when trying to develop a union and intersection contracts.
Section \ref{sec:issues-literature} presents issues and shortcomings found
in existing attempts to solve this problem.
Section \ref{sec:related-work} provides some related work, and Section
\ref{sec:conclusion} concludes.

@@

\section{Features of languages}
\label{sec:feat-lang}
\info{Zoology of various features that we will eventually show
  conflict with this or that property or implementation of union and
  intersection. Including user-define contracts.}

@@

\section{Union \& intersection}
\label{sec:union-inter}
\info{What are they, what are they used for.}

@@

\section{Issues coming from the semantics}
\label{sec:issues-sem}
\info{What goes wrong or difficult when trying to implement union and
  intersection literally}

@@

\section{Issues in concrete restrictions from the literature}
\label{sec:issues-literature}
\info{The various papers and the tradeoffs they make}

@@

\section{Related work}
\label{sec:related-work}
\info{Including a mention of statically typed systems with union}

@@

\section{Conclusion}
\label{sec:conclusion}
